R for Clinical Study Reports and Submission

### 2023-06-05 project-folder.qmd
Update MRAN snapshot links to Posit Public Package Manager snapshot links

# set up repository based on the snapshot date
repos <- paste0("https://mran.microsoft.com/snapshot/", snapshot, "/")

@@

We can also define the package repository to be a specific snapshot date.
For example, we used Microsoft R Application Network (MRAN) to
define the snapshot date to be `2021-08-06`.
The snapshot date freezes the R package repository.

In other words, all R packages installed in this RStudio project
are based on the frozen R version at the snapshot date.
Here it is `2021-08-06` by using the MRAN server.

Below information will be displayed after a new R session is opened.

```
Current project R package repository:
    https://mran.microsoft.com/snapshot/2021-08-06/
```

::: {.callout-note}
Posit Package Manager provides a solution to host both publicly available
and internally developed R packages. However, the
[Posit Public Package Manager](https://packagemanager.posit.co/)
does not provide a daily snapshot as MRAN does.
:::

>>>>

# set up repository based on the snapshot date
repos <- paste0("https://packagemanager.posit.co/cran/", snapshot)

@@

We can also define the package repository to be a specific snapshot date.
For example, we used Posit Public Package Manager to
define the snapshot date to be `2021-08-06`.
The snapshot date freezes the R package repository.

In other words, all R packages installed in this R project
are based on the frozen R version at the snapshot date.
Here it is `2021-08-06` by using the Posit Package Manager.

The information below will be displayed after a new R session is opened.

```
Current project R package repository:
    https://packagemanager.posit.co/cran/2021-08-06
```

::: {.callout-note}
[Posit Public Package Manager](https://packagemanager.posit.co/)
hosts daily CRAN snapshots for Mondays to Fridays of the week.
Posit Package Manager, when deployed internally within an organization,
provides a solution to host both publicly available and internally
developed R packages.
:::

### 2023-06-05 submission-package.qmd
Update MRAN snapshot links to Posit Public Package Manager snapshot links

# # Commented out as the snapshot availability is not guaranteed
# x <- available.packages(contriburl = contrib.url("https://mran.microsoft.com/snapshot/2021-08-06/"))
# df2$version <- x[match(df2$package, x[, "Package"]), "Version"]
df2$version <- c("0.2.0", "2.4.3", "1.0.7", "1.1.3", "1.6.2-1", "0.3.0")

@@

options(repos = "https://mran.microsoft.com/snapshot/2021-08-06/")

>>>>

# # Commented out as the snapshot availability is not guaranteed
# x <- available.packages(contriburl = contrib.url("https://packagemanager.posit.co/cran/2021-08-06"))
# df2$version <- x[match(df2$package, x[, "Package"]), "Version"]
df2$version <- c("0.2.0", "2.4.3", "1.0.7", "1.1.3", "1.6.2-1", "0.3.0")

@@

options(repos = "https://packagemanager.posit.co/cran/2021-08-06")
